output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
nyc_squirrels <- readr::read_csv("Squerrils_data.csv")
#nyc_squirrels <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-29/nyc_squirrels.csv")
library(tidyverse)
library(maps)
library(extrafont)
library(ggalt)
library(ggthemr)
ggthemr("light")

install.packages("ggtext")
devtools::install_github("clauswilke/ggtext")
library(ggtext)
view(nyc_squirrels)
#write_csv(nyc_squirrels,"Squerrils_data.csv")
#library(mapdata)
#library(ggmap)
```

USE THIS
```{r}
#aggregating conditions - able to reorder factor!
#next, create total n? barplot with coordflip?
#how about adding the dates? weekend vs not?
activity_df <- nyc_squirrels %>% 
  gather(key = "activity", value = "condition", c(running:other_interactions))%>%  filter(condition != FALSE & !is.na(condition)) %>% 
  mutate(activity = as.factor(activity)) %>% 
  group_by(activity, shift) %>% 
  summarise(total = n()) %>% 
  ungroup() %>%
  spread(shift, total) %>% 
  mutate(difference = PM-AM) 

activity_df %>% 
  filter(new_activity == "other_activities") %>% 
  view()

condition %>% 
  group_by(new_activity) %>% 
  count(new_activity)

view(condition)

g <- ggplot(activity_df,aes(x = AM, xend = PM, y = fct_reorder(activity ,difference)))+
  geom_dumbbell(colour = "grey60", size = 2,
                colour_x = "#F7BC08", colour_xend = "#395B74")+
    disecr
    labs(x = "Number of Squerrils", y = "Observed activity", title = "What are the squerrils doing in the morning and what in the afternoon?",
         subtitle = paste0(sum(condition$AM),  " central park sqerril's activities were observed by the AM shift, and a total of ", sum(condition$PM), " activities were observed by the PM shift -\nApparently some sqeurrils were 'multi-tasking'"))+
annotate(geom = "text", x = 580, y = "foraging", label = "AM", colour = "#F7BC08", fontface = "bold.italic", size = 5)+
annotate(geom = "text", x = 855, y = "foraging", label = "PM", colour = "#395B74", fontface = "bold.italic", size = 5)+


g +theme(text=element_text(family = "Microsoft Tai Le"))

        
view(activity_df)  


```
ADD: make Title color like Dots and change font.

```{r}
geom_bar(stat = "identity")+
  coord_flip()+
  facet_grid(. ~ shift)+
    geom_text(aes(x = PM, label = total),nudge_y = 50)

view(condition)
str(condition$activity)

#adding the points, but this comes out only on central park?
ggplot(condition ,aes(x= long, y = lat), color = activity)+
  geom_point()+
  facet_grid(. ~ activity)



#number of days reported
n_days <- 
  condition %>% 
  distinct(new_date) %>% 
  mutate(n = n()) %>% 
  length(n)
n_days

#let's look at relation to average:
by_average <- condition %>% 
  group_by(activity) %>%
  mutate(total_activity = length(activity)) %>% 
  ungroup() %>% 
    group_by(activity, new_date) %>% 
    mutate(mean_activity = total_activity/11,
           each_day = n(),
           dis_from_mean = each_day - mean_activity) %>% 
  filter(activity == "indifferent" | activity ==  "runs_from" | activity ==  "tail_twitches") %>%
  group_by(activity, dis_from_mean) %>% 
  distinct(new_date) %>% 
  ungroup()

#not interesting? missing to many points?
ggplot(by_average, aes(x = new_date, y= dis_from_mean))+
  geom_col(aes(fill = ifelse(dis_from_mean < 0, "green", "red")))+
  facet_grid(activity ~ .)

view(by_average)

#counting nmber of activities
by_condition <- condition %>% 
  group_by(new_date, activity) %>% 
  summarise(n= n())



#plotting activitis by number of cases
by_condition %>% 
  ggplot()+
  geom_bar(aes(x= fct_reorder(activity, n), y= n), stat = "identity")+
  coord_flip()+
  facet_grid(. ~ new_date)
  
#how many are repeated?
  condition %>% 
  count(unique_squirrel_id, activity, sort = T)

view(condition)
#how many kinds are there? to filter only to TRUE?
condition %>% 
  count(activity, condition)


#are there anomailes? 1-3
uniques <- condition %>% 
  filter(unique_squirrel_id=="40B-AM-1019-06")
view(uniques)

#a map of nyc
gg1 <- ggplot() + 
  geom_polygon(data = states_new, aes(x = long, y = lat), fill = NA, color = "blue") + 
  coord_quickmap()

#adding the points, but this comes out only on central park?
gg1 +
  geom_point(data = condition, aes(x= long, y = lat))+
  facet_grid(. ~ activity)

view(nyc_squirrels)
```

I created the map above, a data frame to implement but it seems they all fall on central park??

Let's try plotting on a map?
```{r}
states <- map_data("state")
states_new <- states %>% 
  filter(subregion == "manhattan")

gg1 <- ggplot() + 
  geom_polygon(data = states_new, aes(x = long, y = lat), fill = NA, color = "blue") + 
  coord_quickmap()
```




```{r}

usa <- map_data("usa")
gg1 <- ggplot()+
  geom_polygon(data = usa, aes(x = long, y = lat, group = group), fill = "violet", color = "blue")+
  coord_quickmap()

gg1

labs <- tibble(
  long = c(-122.064873, -122.306417),
  lat = c(36.951968, 47.644855),
  names = c("SWFC", "NWFSC")
)
gg1 +
  geom_point (data = labs, aes( x= long, y = lat), fill = "yellow", shape = 21, size = 5)
  
geom_point(data = labs, aes(x = long, y = lat), shape = 21, color = "black", fill = "yellow", size = 5)
```

Ok, now try states:
```{r}
states <- map_data("state") 
head(states)

#plotting the states nicely:
ggplot(data = states)+
  geom_polygon(aes(x= long, y = lat, fill = region, group = group), color = "white")+
  coord_quickmap()+
  guides(fill=FALSE)


ggplot(data = states) + 
  geom_polygon(aes(x = long, y = lat, fill = region, group = group), color = "white") + 
  coord_quickmap() +
  guides(fill = FALSE)  # do this to leave off the color legend
```

how many age criterias do we have?
```{r}
nyc_squirrels %>% 
  count(age, sort= T)

#How about different interactions with humans?

(condition <- nyc_squirrels %>% 
  gather(key = "activity", value = "condition", approaches:runs_from) %>% 
  count(activity, condition))
```

But i'm not sure if they overlap - do they sometimes approache, sometimes indifferent and so forth?